Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-12-03 dsn-2018/bare_conf.tex
Expanded Empirical Results section
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

Table \ref{table:differentials} states the

@@

Refer to Table \ref{table:neighborhood} for the sizes of neighborhoods
of existing collisions. In particular, note that Y. Sasaki's attack--which
claimed to improve upon X. Wang's attack--has a larger neighborhood size, and
likewise with P. Kasselman's attack which improved upon H. Dobbertin's attack.

@@

\subsection{Zeroes \& Ones}

Separate table for known attacks as data points. Examples as appendix.

@@

Include table detailing how many have multicollisions and how many don't.
Hypothesis: all do since all existing datapoints do.

Separate table for known attacks as data points. Examples as appendix.

@@

Include table detailing how many have ASCII blocks and how many don't.

See Table \ref{table:ascii} for results. Note that the validation of
P. Kasselman's and H. Dobbertin's results do not hold for the latter attacks
by X. Wang, Y. Sasaki, or M. Schl{\"a}ffer. Thus, while the latter attacks have
been viewed as being of better quality, under this particular metric,
P. Kasselman's and H. Dobbertin's collision classes are better.

@@

>>>>

Table \ref{table:differentials} states the number of unique differentials,
including the specified one, which produce a differential path conforming to
each of the collision classes. We note in particular that while Y. Sasaki's
attack is generally an improvement upon X. Wang's, Y. Sasaki's attack has fewer
input block differentials and thus less flexibility in this aspect. Further,
M. Schl{\"a}ffer's attack -- also building off the work of X. Wang -- has the
same number of differentials as thus is also more flexible than Y. Sasaki's.

@@

Refer to Table \ref{table:neighborhood} for the sizes of neighborhoods
of existing collisions. In particular, note that both Y. Sasaki's attack and
M. Schl{\"a}ffer's attack -- which both claimed to improve upon X. Wang's
attack--have a larger neighborhood sizes, and likewise with P. Kasselman's
attack which improved upon H. Dobbertin's attack. Thus, the newer collisions
occur in more dense subsets of the collision class space.

@@

\subsection{Zeroes}

See table \ref{table:zeroes} for the maximum count of zeroes in a block
for existing collisions. Note that X. Wang's attack is the leader, with 509
maximum zero bits in the collision pair. Further, while Y. Sasaki improved
the bound in other areas, this was not one of them. Of note too,
H. Dobbertin's and P. Kasselman's collisions are essentially identical in
this metric.

\begin{table}
    \caption{Number of Zeroes in a Colliding Block}
    \label{table:zeroes}
    \begin{tabular}{c c c c}
        \textbf{Attack} & \textbf{Count} & \textbf{Attack} & \textbf{Count} \\
        X. Wang's & 509 & Y. Sasaki's & 494 \\
        H. Dobbertin's & 504 & P. Kasselman's & 504 \\
        M. Schl{\"a}ffer's & 506 & & \\
    \end{tabular}
\end{table}

@@

We note that while these collisions are state independent and include
multicollisions, none of these attacks are always multicollisions. Many of the
blocks we've found only collide under the initial state value. Because of this,
these collisions are only useful if you know the current state where a
colliding pair is to be injected. Thus, this is one area in which collisions
could potentially improve.

@@

See Table \ref{table:ascii} for results of finding ASCII block pairs. Note that
this table validates P. Kasselman's and H. Dobbertin's results of finding
two ASCII block messages. However, these results do not hold for later
collisions by X. Wang, Y. Sasaki, or M. Schl{\"a}ffer. Thus, while the latter
attacks have been viewed as being of better quality, under this particular
metric, P. Kasselman's and H. Dobbertin's collision classes are better.

@@

\subsection{Recapitulation}

Overall, we feel that while the given collision classes have value and utility,
they do not constitute full second preimage attacks. Further, simple
neighborhood search does not lead to collisions in every case. Therefore,
additional techniques are necessary for expanding the collision neighborhood.
